\textbf{Designing a Security Management Layer for CDN Assets}

### 2016-02-12 tex/paper.tex
Added discussion about COW scalability

>>>>

\subsubsection{Copy-on-Write's effect on Scalability}
As no comparison with solutions that were not Copy-on-Write based were made, no scientific
conclusions can be drawn from how its effect was on the scalability of the system. However some
intuitively drawn conclusions can be suggested. If comparing to a system which uses a SQL database
the Copy-on-write system would have an easier time to scale on the width as no global locks or 
transactions has to be used, which with high probability would slow down the system, especially 
when widely distributed. 
The gain of having the locks or transactions would be that the system would always be
in a fully consistent state. The loss would be that all of the database nodes would need to 
constantly have to be fully aware of the state of the other nodes.

\par A more interesting solution would be to not implement any Copy-on-Write system and simply use 
a persistent storage that scales with eventual consistency. That implementation would most likely be
more efficient than the current solution, with MongoDB as a persistent storage and the Copy-on-Write
handling in the back-end code, as a lot of optimisations could be done in the database engine
instead.
